Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-05-13 awipev-CO2.Rmd
adding script for plot poster2

#plot for POSTER june 2019
#plot of S/T
poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 ), aes(x=datetime,y=temp_fb)) +
  geom_point(col="blue", size=0.5 )+
  labs(x = "Time", y="Temperature (°C)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(poster_temp)
ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")

poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb)) +
  geom_point(col="blue", size=0.5 )+
  labs(x = "Time", y="Salinity (PSU)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(poster_sal)
ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")

@@

#plot for POSTER june 2019
#plot of TA calculated from S + discrete
p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
  geom_point(col="blue", size=0.5 )+
  geom_point(aes(y=at, fill= "Reference measured samples"), col="red") +
  labs(x = "Time", y = "Calculated TA from salinity (µmoles/kg)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(p_at_sal)
ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")

>>>>

# #plot for POSTER june 2019
# #plot of S/T
# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
#   geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
#   labs(x = "Time", y="Temperature (°C)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity (PSU)"))
# print(poster_temp)
# par(mar=c(5, 4, 4, 6) + 0.1)
# 
# png("poster_sal_temp.png", width= 900, height=600)
# 
# plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.lab = 3) +
# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)  
# 
#     grid(lty=1)
#   
#    par(new = T)
#  
# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="", axes=FALSE,ylim=c(-2,9))+
# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
#    # axis.POSIXct(1, at=seq(as.Date("2015-09-01"), max =as.Date("2019-09-01"), by="year"), format="%Y") +
# axis.POSIXct(1,d_all$datetime,format(d_all$datetime,"%Y-%m-%d %H:%M:%S",tz="UTC"), major.format = "%Y-%m",labels = format(d_all$datetime, "%Y-%m-d %H:%M:%S"), cex =3)
# 
# mtext("Time",side=1,col="black",line=0.5)  
# legend("topleft", legend=c("Temperature (°C)", "Salinity (PSU)"),
#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
#   #grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
#    #  lwd = "months")
#      box()
#      dev.off()
#      
#      
# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
# 
# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
#   geom_point(col="blue", size=0.5 )+
#   labs(x = "Time", y="Salinity (PSU)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
# print(poster_sal)
# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")

@@

#plot for POSTER june 2019
#plot of TA calculated from S + discrete
p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
  geom_point(col="blue", size=0.5 )+
  geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
  labs(title=  "Calculated TA from salinity (µmoles/kg)", x = "Time", y= "") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position= c(0.7, 0.15), 
                     legend.text=element_text(size=15),
                     plot.title = element_text(vjust = 0.5,size = rel(1.5),margin = margin(t = 10, b = -20)),
                     axis.text=element_text(size=15),
                     legend.title=element_blank())

print(p_at_sal)
ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
